SMT-Boosted Security Types for Low-Level MPC

### 2025-04-28 esop25/slides.tex
checkpoint

  The cvc5 Finite Fields Theory supports automatate satisfiability checking of equational
  constraint definitions $\eqs$ over prime fields $\mathcal{F}_{p}$.

@@

  \begin{itemize}
  \item Generalize verification to arbitrary prime fields.
  \item Automated type system to eliminate manual proof elements.
  \item Support for concurrency.
  \end{itemize}

>>>>

  The cvc5 Finite Fields Theory supports automated satisfiability checking of equational
  constraint definitions $\eqs$ over prime fields $\mathcal{F}_{p}$.

@@

  \begin{itemize}
  \item In this paper: typing verifies noninterference until declassification.
    \begin{itemize}
    \item Goal: accurately verify declassification bounds.
    \end{itemize}
  \item Automated weakest precondition/stongest postcondition inference.
  \item Scalability evaluation of large circuits.
  \item Support for concurrency.
  \end{itemize}
